An IFS study of Low-powered Radio Galaxies

### 2018-01-24 paper.tex
EoDC: abstract written
Finished v0.9 - for my own read through and check

 On branch master
 Changes to be committed:
	modified:   paper.tex
	modified:   produce_maps.py

% Abstract of the paper
\begin{abstract}
This is a simple template for authors to write new MNRAS papers.
The abstract should briefly describe the aims, methods, and main results of the paper.
It should be a single paragraph not more than 250 words (200 words for Letters).
No references should appear in the abstract.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
% keyword1 -- keyword2 -- keyword3
\end{keywords}

>>>>

% Abstract of the paper
\begin{abstract}
The most powerful radio galaxies are well studied with good a good understanding of their formations processes, however they are intrinsically rare objects and not representative of the general population of radio galaxies. Low-powered radio galaxies are comparatively poorly studied with many conflicting viewpoints regarding their origin and the extent of the effect of feedback from them.

In this paper, we present a complete sample of 11 nearby low-powered radio galaxies, observed with a suite of instruments. This paper focuses on the spatially-resolved stellar kinematics, stellar populations, and ionized gas distribution, kinematics and ionization derived from optical IFS observations. We compare the characteristics and properties of our sample to those of ordinary (i.e.\ optically-selected) ETGs from the Atlas$^\text{3D}$ and MASSIVE IFS surveys. These include the fast/slow rotator classification fraction, kinematic substructures, absorption line strength radial gradients, general stellar population properties, ionized gas distribution and kinematics and the dominant source of ionizing photons.

We tentatively find that our radio-selected ETGs contain a higher mass in of ionized gas than expected from optically-selected ETGs, but after accounting for the differences in the mass distribution, we find no further differences between the two samples in the characteristics that can be studied with optical IFU data. We suggest that this is consistent with the notion that low-powered radio galaxies are ordinary ETGs experiencing a brief active phase which maintains their low star-formation rates (also known as maintenance or jet-mode AGN). 
\end{abstract}

\begin{keywords}
galaxies: kinematics and dynamics -- galaxies: abundances -- galaxies: active -- galaxies: jets -- galaxies: structure
\end{keywords}
